Environmental Factors Affecting Water Quality at Toronto Beaches

### 2024-09-27 paper/paper.qmd
Beautification tables

# Appendix {#appendix-a}
## Variable description{#appendix-a.1}
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-sum1
#| fig-cap: "Variable description"

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-sum3
#| fig-cap: "Summary numerical variables"

@@

summary_stats %>%
  kable(
    col.names = c("Variable", "Mean", "SD", "Min", "Median", "Max"), 
    booktabs = TRUE,  
    align = c("l", "c", "c", "c", "c", "c"),   
    format.args = list(big.mark = ",")  
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"), 
    full_width = F,   
    position = "center",   
    font_size = 10   
  ) %>%
  row_spec(0, bold = TRUE, background = "lightgray", color = "black") %>%  # Style header row
  footnote(general = "Summary statistics for Wind Speed, Air Temperature, Water Temperature, Fowl Count, and Turbidity.")
```

>>>>

# Appendix {#appendix-a}
## Variable description{#appendix-a.1}
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-sum1
#| fig-cap: "Key Variable Description"

@@

```
\newpage
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-sum3
#| fig-cap: "Summary numerical variables"

@@

summary_stats %>%
  kable(
    col.names = c("Variable", "Mean", "SD", "Min", "Median", "Max"), 
    booktabs = TRUE,  
    align = c("l", "c", "c", "c", "c", "c"),   
    format.args = list(big.mark = ",")  
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"), 
    full_width = F,   
    position = "center",   
    font_size = 10
  ) %>%
  row_spec(0, bold = TRUE, background = "lightgray", color = "black") %>%  # Style header row
  column_spec(1, bold = TRUE, width = "9em") %>%    # Set width and style for Variable
  column_spec(2:6, width = "6em") %>%    # Set width for the rest column
  footnote(general = "Summary statistics for Wind Speed, Air Temperature, Water Temperature, Fowl Count, and Turbidity.")
